Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Update..

\documentclass[11pt,sigplan,screen,nonacm]{acmart}
% \documentclass[11pt,conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% \usepackage[sort,nocompress]{cite}
\usepackage{natbib}
\setcitestyle{square, comma, numbers,sort&compress, super}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

We designed a \texttt{BlockchainAdapter} interface, which exposes the following APIs externally to the coordinator and the cohort:
\begin{itemize}
  \item \texttt{StartVoting(transaction\_id, cohorts, vote\_timeout\_time)}\\Called by the coordinator to start voting on a transaction. \texttt{cohorts} is the number of cohorts that will vote on this transaction later. \texttt{vote\_timeout\_time} is the absolute time on the blockchain when the 2PC stops taking votes.
  \item \texttt{Vote(transaction\_id, cohort\_id, ballot)}\\Called by the cohort to vote \texttt{COMMIT} or \texttt{ABORT} on a transaction before timeout.
  \item \texttt{GetVotingDecision(transaction\_id)}\\Called by any component to check the voting state of a transaction.
\end{itemize}

@@

\subsubsection{Cohort} \label{cohort}
The cohort exposes two APIs to the coordinator:
\begin{itemize}
  \item \texttt{PrepareTransaction(\\PrepareTransactionRequest, PrepareTransactionResponse)}
  \item \texttt{GetTransactionResult(\\GetTransactionResultRequest, GetTransactionResultResponse)}
\end{itemize}

@@

While testing in the Truffle development, we learned the gas used for successfully committing a transaction with two cohorts is around 0.33 USD \cite{gwei} (see \ref{appendix} for breakdowns).

@@

\appendix
\label{appendix}
\begin{table}[hbtp]
  \centering
  \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  \label{table:cost}
  \begin{tabular}{|l|c|c|c|}
    \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
    StartVoting &73441 &0.000073441 & 0.143\\
    \hline
    Vote 1 &56451	&0.000056451 &0.110\\
    \hline
    Vote 2 &39513 &0.000039513 &0.077\\
    \hline
    Total &169405 &0.000169405 &0.330\\
    \hline
  \end{tabular}
\end{table}
\end{document}
\endinput

>>>>

\documentclass[11pt,sigplan,screen,nonacm]{acmart}
% \documentclass[11pt,conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% \usepackage[sort,nocompress]{cite}
\usepackage{natbib}
\setcitestyle{square, comma, numbers,sort&compress, super}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage[toc,page]{appendix}
\usepackage{algorithmic}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

We designed a \texttt{BlockchainAdapter} interface, which exposes the following APIs externally to the coordinator and the cohort:
\begin{itemize}
  \item \texttt{StartVoting(transaction\_id, cohorts, vote\_timeout\_time)}\\Called by the coordinator to start voting on a transaction. \texttt{cohorts} is the number of cohorts that will vote on this transaction later.\\\texttt{vote\_timeout\_time} is the absolute time on the blockchain when the 2PC stops taking votes.
  \item \texttt{Vote(transaction\_id, cohort\_id, ballot)}\\Called by the cohort to vote \texttt{COMMIT} or \texttt{ABORT} on a transaction before timeout.
  \item \texttt{GetVotingDecision(transaction\_id)}\\Called by any component to check the voting state of a transaction.
\end{itemize}

@@

\subsubsection{Cohort} \label{cohort}
The cohort exposes two APIs to the coordinator:
\begin{itemize}
  \item \texttt{PrepareTransaction(\\PrepareTransactionRequest,\\PrepareTransactionResponse)}
  \item \texttt{GetTransactionResult(\\GetTransactionResultRequest,\\GetTransactionResultResponse)}
\end{itemize}

@@

While testing in the Truffle development, we learned the gas used for successfully committing a transaction with two cohorts is around 0.33 USD \cite{gwei} (see Appendix \ref{appendix:blockchaingas} for breakdowns).

@@

% \appendix
% \begin{table}[hbtp]
  % \centering
  % \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  % \label{table:cost}
  % \begin{tabular}{|p{1.8cm}|p{1.8cm}|p{2cm}|p{1.8cm}|}
    % \hline
          % & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          % \hline
    % StartVoting &73441 &0.000073441 & 0.143\\
    % \hline
    % Vote 1 &56451	&0.000056451 &0.110\\
    % \hline
    % Vote 2 &39513 &0.000039513 &0.077\\
    % \hline
    % Total &169405 &0.000169405 &0.330\\
    % \hline
  % \end{tabular}
% \label{blockchaingas}
% \end{table}

\begin{appendices}

  \section{Blockchain Gas Used}
  \label{appendix:blockchaingas}

  \begin{table}[hbtp]
    \centering
    \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
    \label{table:cost}
    \begin{tabular}{|p{1.8cm}|p{1.8cm}|p{2cm}|p{1.8cm}|}
      \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
      StartVoting &73441 &0.000073441 & 0.143\\
      \hline
      Vote 1 &56451	&0.000056451 &0.110\\
      \hline
      Vote 2 &39513 &0.000039513 &0.077\\
      \hline
      Total &169405 &0.000169405 &0.330\\
      \hline
    \end{tabular}
  \end{table}

\end{appendices}

\end{document}
\endinput
